Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-19 paper/paper.tex
revised content added to semantics section. Checkpointing
checkpointing; outlined remainder of semantics section
Add section on testing

\lstdefinestyle{agree}
{frame=none,
  basicstyle=\ttfamily,
  language=ML,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  numbers=none,
  numberstyle=\tiny\color{gray},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=false,
  breakatwhitespace=true,
  tabsize=2,
  linewidth=2\linewidth,
  morecomment=[l]{--},
  escapeinside={*}{*},
  morekeywords={eq, bool, guarantee, assume, true, false, pre, not, and, or, property, const, Historically, Since, Once, event}
}

@@

\newcommand{\konst}[1]{\ensuremath{\mathsf{#1}}}
\newcommand{\imp}{\Rightarrow}
\newcommand{\lval}{\ensuremath{\mathit{lval}}}
\newcommand{\set}[1]{\ensuremath{\{ {#1} \}}}
\newcommand{\kstar}[1]{\ensuremath{{#1}^{*}}}
\newcommand{\Lang}[1]{\ensuremath{{\mathcal L}({#1})}}
\newcommand{\LangTheta}[1]{\ensuremath{{\mathcal L}_{\theta}({#1})}}
\newcommand{\itelse}[3]{\mbox{$\mathtt{if}\ {#1}\ \mathtt{then}\ {#2}\ \mathtt{else}\ {#3}$}}

@@

\section{Illustrative Example}
\label{sec:example}
\input{example}

@@

\section{Assume-Guarantee Reasoning in AGREE}
\label{sec:agree}
\input{agree}

@@

\section{AGREE Semantics for Component Synthesis}
\label{sec:semantics}
\input{semantics}

@@

\section{Synthesis to CakeML and Proof Sketch}
\label{sec:synthesis}
\input{synthesis}

@@

\section{Case Studies}
\label{sec:case-study}
\input{case-study}

@@

\section{Related Work}
\label{sec:related-work}
\input{related-work}

>>>>

\lstdefinestyle{agree}
{frame=none,
  basicstyle=\ttfamily,
  language=ML,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  numbers=none,
  numberstyle=\tiny\color{gray},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=false,
  breakatwhitespace=true,
  tabsize=2,
  linewidth=2\linewidth,
  morecomment=[l]{--},
  escapeinside={*}{*},
  morekeywords={eq, bool, guarantee, assume, true, false, pre, not, and, or, property, const, Historically, Since, Once, event, annex, Implementation, process, subcomponents}
}

@@

\newcommand{\konst}[1]{\ensuremath{\mathsf{#1}}}
\newcommand{\imp}{\Rightarrow}
\newcommand{\set}[1]{\ensuremath{\{ {#1} \}}}
\newcommand{\sem}[1]{\ensuremath{[\![ #1 ]\!]}}
\newcommand{\kstar}[1]{\ensuremath{{#1}^{*}}}
\newcommand{\Lang}[1]{\ensuremath{{\mathcal L}({#1})}}
\newcommand{\itelse}[3]{\mbox{$\mathtt{if}\ {#1}\ \mathtt{then}\ {#2}\ \mathtt{else}\ {#3}$}}

@@

\section{Illustrative example}
\label{sec:example}
\input{example}

@@

\section{Assume-guarantee reasoning in AGREE}
\label{sec:agree}
\input{agree}

@@

\section{AGREE semantics for component synthesis}
\label{sec:semantics}
\input{semantics}

@@

\section{Synthesis to CakeML}
\label{sec:synthesis}
\input{synthesis}

@@

\section{Testing Specifications with AGREE}
\label{sec:testing}
\input{testing}

\section{Case studies}
\label{sec:case-study}
\input{case-study}

@@

\section{Related work}
\label{sec:related-work}
\input{related-work}
